A decision support tool for the Home Health Care Routing and Scheduling Problem

### 2022-02-21 tex/Paper/main.tex
updated main.tex
made changes to CalculateJobTimes pseudocode.

\begin{algorithm}[h]
\footnotesize
\caption{\textsc{CalculateJobTimes}$(i, r_i)$}
\label{alg:cjt}
\begin{algorithmic}[1]
	\State Let $f$ be the initial shift for nurse $i$
	\State $a(i,k_{0}^i) \gets 0$
%	\For{$j \gets 1 \To m_i$}
	\For{$j \in r_i$}
		\State $a(i,j) \gets a(i, j-1) + w_{ij-1} + s_{j-1} + T_i(j-1, j)$
		\If{$\max\{a(i,j), e_j\} + s_j > v(\pi_{f}^{i}) \AAnd f \neq g_i$}
			\State feasible, $t_j, w_{ij}, z_j, \tilde{z}_j, f \gets$ \textsc{FindValidTime}($i,j,f, a(i,j)$)
			\If{feasible $= \False$}
				\Break
			\Else \hspace{0.2mm} \textbf{continue}
				%\Continue
			\EndIf
			%\State $t_j, f \gets$ \textsc{FindValidTime}$(i, j, f, a(i,j))$
			%\State $w_{ij} \gets t_j - a(i,j)$
			%\State $z_j \gets t_j - l_j$
%			\State $f \gets$ shift containing time $t_j$
		\ElsIf{$a(i,j) > v(\pi_{f}^{i}) \AAnd a(i,j) < u(\pi_{f+1}^{i}) \AAnd f \neq g_i$}
			\State $v \gets v(\pi_{f}^{i})$
			\State feasible, $t_j, w_{ij}, z_j, \tilde{z}_j, f \gets$ \textsc{FindValidTime}($i,j,f,v$)
			\If{feasible $= \False$}
				\Break
			\Else \hspace{0.2mm} \textbf{continue}
				%\Continue
			\EndIf
			%\State $t_j, f \gets$ \textsc{FindValidTime}$(i,j, f, v)$
			%\State $w_{ij} \gets t_j - v$
			%\State $z_j \gets t_j - l_j$
%			\State $f \gets$ shift containing time $t_j$
		\Else
			\State $w_{ij} \gets \max\{0, (e_j-a(i,j))\}$
			\State $z_j \gets \max\{0, (a(i,j) - l_j)\}$
			\State $t_j \gets a(i,j) + w_{ij}$
		\EndIf
	\EndFor
	\Return either statement of infeasibility or feasible schedule for nurse $i$
\end{algorithmic}
\end{algorithm}

@@

@@

				\If{$l_j^{(j')} > t_{j'}$} % job j occurs after job j', gap tardiness allowed

@@

\begin{figure}[htb!]
    \centering
    \includegraphics[width=0.7\textwidth]{images/scheme}
    \caption{Scheme of the proposed GRASP algorithm.}
    \label{fig:graspdiagram}
\end{figure}

@@

\begin{comment}
\begin{algorithm}[htbp!]
\footnotesize
\caption{\chng{ROUGH FIND VALID TIME ALG}}
\label{alg:roughfvt}
\begin{algorithmic}[1]
\State $\tilde{f} \gets f$, $\tilde{a}(i,j) \gets a(i,j)$, valid $\gets \False$, 
\State DS $\gets \False$, DJ $\gets \False$, secondN $\gets \False$, jType $\gets$ NULL
\State gap $\gets \False$
\If{$j \in J'$}
\State $j' \gets D(j)$ % D : J' -> DJ, returns other job in pair with job j
\State $i' \gets NJ(j')$ % NJ : J -> N, returns the nurse assigned to the job j
\If{$i$ appears later than $i'$ in $\mathcal{O}$}
\State secondN $\gets \True$
\EndIf
\If{$(j, j') \in DS$}
\State DS $\gets \True$
\If{secondN $= \True \AAnd \tilde{a}(i,j) > t_{j'}$} %can also use l_j^(j'), latest ST allowed for j based on j'
\State valid $\gets \False$, infeasible, EXIT
\EndIf % arrival later than latest start time
\Else 
\State $DJ \gets \True$
\If{secondN $= \False$}
\State original TWs are used
\ElsIf{secondN $= \True$} % This nurse is the 2nd one to be assessed, other job has been done
%Need to find out if this job j is before or after j' in the schedule
\State $[e_j^{(j')}, l_j^{(j')}] \gets$ dependent time window, based on $t_j'$ set by $i'$
\If{$\tilde{a}(i,j) > l_j^{(j')} \AAnd$gap $= \False$} % current time is later than latest allowed start based on start time of j' and no gap tard allowed
\State valid $\gets \False$, infeasible, EXIT
\EndIf
\EndIf % i appears later than i' in O
\EndIf %(j, j') in DS
\EndIf %if j in J'
\While{$\Not$ valid}
\State $\tilde{f} \gets \tilde{f}+1$
\State $\tilde{a}(i,j) \gets u(\pi_{\tilde{f}}^{i})$
\If{DS $= \True$}
%\If{secondN $= \True \AAnd \tilde{a}(i,j) > t_{j'}$}
\If{secondN $= \True$}
\If{$\tilde{a}(i,j) > t_{j'}$}
\State valid $\gets \False$, infeasible, EXIT
\ElsIf{$\tilde{a}(i,j) + s_j > v(\pi_{\tilde{f}}^{i}) \AAnd \tilde{f} \neq g_i$}
\Continue
\Else
\State valid $\gets \True$ etc...
\EndIf
\ElsIf{secondN $= \False$}
\If{$\tilde{a}(i,j) + s_j > v(\pi_{\tilde{f}}^{i}) \AAnd \tilde{f} \neq g_i$}
\Continue
\Else
\State valid $\gets \True$ etc...
\EndIf
\EndIf
\ElsIf{DJ $= \True$}
\If{secondN $= \True$}
\If{$\tilde{a}(i,j) > l_j^{(j')} \AAnd$gap $= \False$} % past TW and no gap tard allowed
\State valid $\gets \False$, infeasible, EXIT
\ElsIf{$\max\{\tilde{a}(i,j), e_j^{(j')}\} + s_j > v(\pi_{\tilde{f}}^i) \AAnd \tilde{f} \neq g_i$}%\tilde{a}(i,j) is before or within TW, so check if job can be done in shift
\Continue
\Else
\State valid $\gets \True$ etc...
\EndIf
\ElsIf{secondN $= \False$}
\If{$\tilde{a}(i,j) + s_j > v(\pi_{\tilde{f}}^{i}) \AAnd \tilde{f} \neq g_i$}
\Continue
\Else
\State valid $\gets \True$ etc...
\EndIf
\EndIf
\EndIf % End if DS/DJ is True
\EndWhile
\end{algorithmic}
\end{algorithm}
\end{comment}

>>>>

\begin{algorithm}[h]
\footnotesize
\caption{\textsc{CalculateJobTimes}$(i, r_i)$}
\label{alg:cjt}
\begin{algorithmic}[1]
	\State Let $f$ be the initial shift for nurse $i$
	\State $a(i,k_{0}^i) \gets 0$
%	\For{$j \gets 1 \To m_i$}
	\For{$j \in r_i$}
		\State $a(i,j) \gets a(i, j-1) + w_{ij-1} + s_{j-1} + T_i(j-1, j)$
		\If{$j \in J'$}
			\State $j' \gets D(j)$ % D : J' -> DJ, returns other job in pair with job j
			\State $i' \gets NJ(j')$ % NJ : J -> N, returns the nurse assigned to the job j
			\If{$i$ appears later than $i'$ in $\mathcal{O}$}
				\State secondN $\gets \True$
			\EndIf
			\If{$(j, j') \in DS$}
				\State DS $\gets \True$
				\If{secondN $= \True \AAnd \tilde{a}(i,j) > t_{j'}$} %can also use l_j^(j'), latest ST allowed for j based on j'
					\Return feasible $\gets \False$
				\EndIf % arrival later than latest start time
			\Else 
				\State $DJ \gets \True$
				\If{secondN $= \True$} % This nurse is 2nd one to be assessed, other job has been done
				%Need to find out if this job j is before or after j' in the schedule
					\State $[t_{j'} + e_j^{(j')}, t_{j'} + l_j^{(j')}] \gets$ dependent time window, based on $t_{j'}$ set by $i'$
					\If{$\tilde{a}(i,j) > t_{j'} + l_j^{(j')} \AAnd$gap $= \False$} % current time is later than latest allowed start based on start time of j' and no gap tard allowed
						\Return feasible $\gets \False$
					\ElsIf{$\tilde{a}(i,j) > t_{j'} + l_{j}^{(j')} \AAnd$gap $= \True$}
						\If{$t_{j'} + l_{j}^{(j')} < t_{j'}$} %job j occurs before job j', gap too small
							\Return feasible $\gets \False$
						\EndIf
					\EndIf
				\EndIf % i appears later than i' in O
			\EndIf %(j, j') in DS
		\EndIf %if j in J'
		\If{$\max\{a(i,j), e_j\} + s_j > v(\pi_{f}^{i}) \AAnd f \neq g_i$}
			\State feasible, $t_j, w_{ij}, z_j, \tilde{z}_j, f \gets$ \textsc{FindValidTime}($i,j,f, a(i,j)$)
			\If{feasible $= \False$}
				\Break
			\Else \hspace{0.2mm} \textbf{continue}
				%\Continue
			\EndIf
		\ElsIf{$a(i,j) > v(\pi_{f}^{i}) \AAnd a(i,j) < u(\pi_{f+1}^{i}) \AAnd f \neq g_i$}
			\State $v \gets v(\pi_{f}^{i})$
			\State feasible, $t_j, w_{ij}, z_j, \tilde{z}_j, f \gets$ \textsc{FindValidTime}($i,j,f,v$)
			\If{feasible $= \False$}
				\Break
			\Else \hspace{0.2mm} \textbf{continue}
				%\Continue
			\EndIf
		\Else
			\State $w_{ij} \gets \max\{0, (e_j-a(i,j))\}$
			\State $z_j \gets \max\{0, (a(i,j) - l_j)\}$
			\State $t_j \gets a(i,j) + w_{ij}$
		\EndIf
	\EndFor
	\Return either statement of infeasibility or feasible schedule for nurse $i$
\end{algorithmic}
\end{algorithm}

@@

				\ElsIf{$\tilde{a}(i,j) > t_{j'} + l_{j}^{(j')} \AAnd$gap $= \True$}
					\If{$t_{j'} + l_{j}^{(j')} < t_{j'}$} %job j occurs before job j', gap too small

@@

				\If{$t_{j'} + l_j^{(j')} > t_{j'}$} % job j occurs after job j', gap tardiness allowed

@@

\begin{figure}[htb!]
    \centering
    \includegraphics[width=0.7\textwidth]{figures/scheme}
    \caption{Scheme of the proposed GRASP algorithm.}
    \label{fig:graspdiagram}
\end{figure}

@@

\begin{comment}
\begin{algorithm}[htbp!]
\footnotesize
\caption{\chng{ROUGH FIND VALID TIME ALG}}
\label{alg:roughfvt}
\begin{algorithmic}[1]
\State $\tilde{f} \gets f$, $\tilde{a}(i,j) \gets a(i,j)$, valid $\gets \False$, 
\State DS $\gets \False$, DJ $\gets \False$, secondN $\gets \False$, jType $\gets$ NULL
\State gap $\gets \False$
\If{$j \in J'$}
\State $j' \gets D(j)$ % D : J' -> DJ, returns other job in pair with job j
\State $i' \gets NJ(j')$ % NJ : J -> N, returns the nurse assigned to the job j
\If{$i$ appears later than $i'$ in $\mathcal{O}$}
\State secondN $\gets \True$
\EndIf
\If{$(j, j') \in DS$}
\State DS $\gets \True$
\If{secondN $= \True \AAnd \tilde{a}(i,j) > t_{j'}$} %can also use l_j^(j'), latest ST allowed for j based on j'
\State valid $\gets \False$, infeasible, EXIT
\EndIf % arrival later than latest start time
\Else 
\State $DJ \gets \True$
\If{secondN $= \False$}
\State original TWs are used
\ElsIf{secondN $= \True$} % This nurse is the 2nd one to be assessed, other job has been done
%Need to find out if this job j is before or after j' in the schedule
\State $[e_j^{(j')}, l_j^{(j')}] \gets$ dependent time window, based on $t_j'$ set by $i'$
\If{$\tilde{a}(i,j) > l_j^{(j')} \AAnd$gap $= \False$} % current time is later than latest allowed start based on start time of j' and no gap tard allowed
\State valid $\gets \False$, infeasible, EXIT
\EndIf
\EndIf % i appears later than i' in O
\EndIf %(j, j') in DS
\EndIf %if j in J'
\While{$\Not$ valid}
\State $\tilde{f} \gets \tilde{f}+1$
\State $\tilde{a}(i,j) \gets u(\pi_{\tilde{f}}^{i})$
\If{DS $= \True$}
%\If{secondN $= \True \AAnd \tilde{a}(i,j) > t_{j'}$}
\If{secondN $= \True$}
\If{$\tilde{a}(i,j) > t_{j'}$}
\State valid $\gets \False$, infeasible, EXIT
\ElsIf{$\tilde{a}(i,j) + s_j > v(\pi_{\tilde{f}}^{i}) \AAnd \tilde{f} \neq g_i$}
\Continue
\Else
\State valid $\gets \True$ etc...
\EndIf
\ElsIf{secondN $= \False$}
\If{$\tilde{a}(i,j) + s_j > v(\pi_{\tilde{f}}^{i}) \AAnd \tilde{f} \neq g_i$}
\Continue
\Else
\State valid $\gets \True$ etc...
\EndIf
\EndIf
\ElsIf{DJ $= \True$}
\If{secondN $= \True$}
\If{$\tilde{a}(i,j) > l_j^{(j')} \AAnd$gap $= \False$} % past TW and no gap tard allowed
\State valid $\gets \False$, infeasible, EXIT
\ElsIf{$\max\{\tilde{a}(i,j), e_j^{(j')}\} + s_j > v(\pi_{\tilde{f}}^i) \AAnd \tilde{f} \neq g_i$}%\tilde{a}(i,j) is before or within TW, so check if job can be done in shift
\Continue
\Else
\State valid $\gets \True$ etc...
\EndIf
\ElsIf{secondN $= \False$}
\If{$\tilde{a}(i,j) + s_j > v(\pi_{\tilde{f}}^{i}) \AAnd \tilde{f} \neq g_i$}
\Continue
\Else
\State valid $\gets \True$ etc...
\EndIf
\EndIf
\EndIf % End if DS/DJ is True
\EndWhile
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[h]
\footnotesize
\caption{\textsc{CalculateJobTimes}$(i, r_i)$}
\label{alg:cjtold}
\begin{algorithmic}[1]
\State Let $f$ be the initial shift for nurse $i$
\State $a(i,k_{0}^i) \gets 0$
%	\For{$j \gets 1 \To m_i$}
\For{$j \in r_i$}
\State $a(i,j) \gets a(i, j-1) + w_{ij-1} + s_{j-1} + T_i(j-1, j)$
\If{$\max\{a(i,j), e_j\} + s_j > v(\pi_{f}^{i}) \AAnd f \neq g_i$}
\State feasible, $t_j, w_{ij}, z_j, \tilde{z}_j, f \gets$ \textsc{FindValidTime}($i,j,f, a(i,j)$)
\If{feasible $= \False$}
\Break
\Else \hspace{0.2mm} \textbf{continue}
%\Continue
\EndIf
%\State $t_j, f \gets$ \textsc{FindValidTime}$(i, j, f, a(i,j))$
%\State $w_{ij} \gets t_j - a(i,j)$
%\State $z_j \gets t_j - l_j$
%			\State $f \gets$ shift containing time $t_j$
\ElsIf{$a(i,j) > v(\pi_{f}^{i}) \AAnd a(i,j) < u(\pi_{f+1}^{i}) \AAnd f \neq g_i$}
\State $v \gets v(\pi_{f}^{i})$
\State feasible, $t_j, w_{ij}, z_j, \tilde{z}_j, f \gets$ \textsc{FindValidTime}($i,j,f,v$)
\If{feasible $= \False$}
\Break
\Else \hspace{0.2mm} \textbf{continue}
%\Continue
\EndIf
%\State $t_j, f \gets$ \textsc{FindValidTime}$(i,j, f, v)$
%\State $w_{ij} \gets t_j - v$
%\State $z_j \gets t_j - l_j$
%			\State $f \gets$ shift containing time $t_j$
\Else
\State $w_{ij} \gets \max\{0, (e_j-a(i,j))\}$
\State $z_j \gets \max\{0, (a(i,j) - l_j)\}$
\State $t_j \gets a(i,j) + w_{ij}$
\EndIf
\EndFor
\Return either statement of infeasibility or feasible schedule for nurse $i$
\end{algorithmic}
\end{algorithm}

\end{comment}
